### 2023-10-06 main.tex
proof

   \mathcal{S}_{2}^{-1}=\mathbbm{1}+\sum_{a=1}^{N-1}\beta_{a}e_{aN}

{\color{blue}
\begin{equation}
  \mathcal{S}_{2}^{-1} |\mu\rangle= |\mu\rangle+\delta_{N,\tau}\sum_{a=1}^{N-1}\beta_a|a\rangle
\end{equation} 
\begin{equation}
  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)
\end{equation} 
\begin{equation}
  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\prod_{i=1}^L\left[ \delta_{\tau_i,\mu_i}+\delta_{N,\mu_i}\beta_{\tau_i} (1-\delta_{\tau_i,N})\right]
\end{equation}

We introduce the following notation
\begin{equation}\label{notation1}
    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
and 
\begin{equation}\label{notation2}
    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
    \end{equation}
    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that

@@

where, $\forall x\in\{1,\ldots,L\}$, we have introduced

@@

where $i\in\{1,\ldots,L\}$. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.

@@

The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
To find these quantities we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$. Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}}

Therefore, we have that 
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}
	\end{split}
\end{equation}
For a fixed configuration $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$, using equation \eqref{ResulsBasis} and observing that 
\begin{equation}
  \left(1+\sum_{j=y}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},N})\right)
\end{equation}
we obtain 
    \begin{equation}
\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{j},N})\right)\right)^{1-\delta_{\tau_{y},N}}
\end{equation}
Introducing
\begin{equation}
	c_{y}\in\{0,1\} \qquad \forall y\in \{1,\ldots L\}
\end{equation}
and replacing $\Psi^{'}(\bm{\tau})$ computed above in \eqref{ABS_intermediate} we obtain

%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},N})}
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}

>>>>

   \mathcal{S}_{2}^{-1}=\mathbbm{1}+\sum_{a=1}^{N-1}\beta_{a}e_{aN}\co
which action on the occupation variable of a site is 
  \mathcal{S}_{2}^{-1} |\mu\rangle= |\mu\rangle+\delta_{N,\mu}\sum_{a=1}^{N-1}\beta_a|a\rangle\dt
Therefore, taking the tensor product over the chain we obtain 
  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)
By projecting over a vector $\langle \bm{\tau}|$ we have 
\begin{equation}\label{goodTP-S2}
  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\prod_{i=1}^L\left[ \delta_{\tau_i,\mu_i}+\delta_{N,\mu_i}\beta_{\tau_i} (1-\delta_{\tau_i,N})\right]
For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, using equation \eqref{ResulsBasis} and observing that 
	\left(1+\sum_{j=y}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\mu_{y},N})\right)
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\dt
Introducing $c_{x}$ defined as 
	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}
\begin{equation}\label{coefficients-psiSec}
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{y}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.
We introduce the following notation
\begin{equation}\label{notation1}
    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
\begin{equation}\label{notation2}
    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that

@@

We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ the configuration 

@@

	\end{cases}\dt
 This is a new configuration where  $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ with $N$ and leaves the others sites with the same occupation.  The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.

@@

The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
To find these quantities we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$. Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
\begin{equation}
	\begin{split}
\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
  \\&+
  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}}
	\end{split}
\end{equation}
\end{comment}
By considering a fixed $\langle\bm{\tau}|$, by taking \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients \eqref{coefficients-psiSec} and by using \eqref{goodTP-S2} we write 
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
	\end{split}
\end{equation}

Therefore, we have that equation \eqref{ABS_intermediate} becomes

%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},N})}
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}
